A Theory of Bidirectional Type Synthesis for Simple Types

### 2023-06-27 tex/sec2-outline.tex
[ tex ] Add an overview figure in S2

>>>>

\begin{figure}
  \begin{tikzpicture}
  \matrix (m) [matrix of math nodes, row sep=3em, column sep=10em]
  {
    \boxed{\erase{\Gamma} \vdash \isTerm{t}}   & \boxed{\erase{\Gamma} \vdash \isTerm{t}^{\syn}} \\
    \boxed{\Gamma \vdash \isTerm{t} : A} & \boxed{\Gamma \vdash \isTerm{t} \syn A} \\
  };
  \path[->]
      (m-1-1) edge node [above,align=center] {mode preprocessing} (m-1-2)
              edge node [left,align=left]  {type\\synthesis} (m-2-1)
      (m-1-2) edge node [right,align=right] {bidirectional\\type synthesis} (m-2-2)
      (m-2-1) edge[bend right=8] node [below] {completeness} (m-2-2);
  \path[->]
      (m-2-2) edge[bend right=8] node [above] {soundness} (m-2-1);
  \end{tikzpicture}
  \caption{An implementation of type synthesis via bidirectional typing}
\end{figure}
